%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Senior DevOps Engineer} % Job title
  {NEP The Netherlands, BV.} % Organization
  {Hilversum, Netherlands} % Location
  {Mar. 2021 - Current} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Trained development teams on how to take ownership and handle their own resources in the spirit of the DevOps culture.}
      \item {Used interpersonal and communication skills in interactions, enriching team collaboration, customer relationships on infrastructure as code projects. (Scrum, Jira, Ansible, Terraform)}
      \item {Mentored DevOps engineers on technical best practices. (Ansible, Terraform)}
      \item {Designed and developed forward-thinking systems that meet user needs and improve productivity. (Kubernetes, Rancher, GCP)}
      \item {Created proofs of concept for innovative new solutions. (Docker, Kubernetes, Rancher, GCP)}
      \item {Built fully automated CI/CD pipelines on GitHub Actions for applications builds and deployments. (Docker, GitHub Actions, Kubernetes}
      \item {Improved process and handling automation for infra tools. (Docker, Spinnaker, Kubernetes)}
    \end{cvitems}
  }

%---------------------------------------------------------    
\cventry
{Founder \& Software Engineer} % Job title
{Boxitonline B.V.} % Organization
{Amsterdam, Netherlands} % Location
{Nov. 2019 - Jan. 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Led the team from drafting the idea to implementing the prototype implementation and market launch.}
    \item {Created organization's mission and vision statements for use by employees.}
    \item {Wrote financial forecasts and fund request applications to the European Community.}
    \item {Implemented peer-to-peer marketplace website for temporary storage rental.}
    \item {Built and deployed overall service infrastructure utilizing Heroku and nginx API gateway. (Nodejs, React, Serverless)}
    \item {Conducted target market research to scope out industry competition and identify advantageous trends. (Google Analytics)}
    \item {Created and monitored promotional approaches to increase sales and profit levels. (Google Analytics, HotJar)}
  \end{cvitems}  
}  

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Vandebron, BV.} % Organization
    {Amsterdam, Netherlands} % Location
    {Apr. 2018 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented solutions for platform resiliency and disaster recovery for business continuity, involving systems duplication, load balancing and multi-region deployments. (Azure, AWS)}
        \item {Collaborated closely with product development teams and other stakeholders, using effective communication and active listening skills. (Slack, Jira, Scrum)}
        \item {Designed an overall service architecture and pipelines of the frontend with a micro-services architecture approach. (Nodejs, Scala, Docker)}
        \item {Migrated all the existing services from a VM based architecture onto docker containers running on a custom infrastructure. (D2iQ, Docker, Nodejs, Bash)}
        \item {Built fully automated CI/CD pipelines to build and deploy the frontend and backend applications. (Jenkins, GitHub Actions, Nodejs, Groovy)}
        \item {Integrated Azure logs with a centralized logging environment which gather log data from Azure resources. (Elasticsearch, Logstash, Kibana)}
        \item {Maintained and expanded the infrastructure lifecycle in a IaC fashion, using Ansible and Terraform to deploy on AWS cloud. (Ansible, Terraform, EC2, S3)}
      \end{cvitems}
    }
      
%---------------------------------------------------------
  \cventry
    {Salesforce Developer} % Job title
    {Vandebron, BV.} % Organization
    {Amsterdam, Netherlands} % Location
    {Jul. 2017 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated with Customer Service to identify and support business process requirements and development needs.}
        \item {Selected, trained and onboarded new team members, explaining the current system design and leading them during development of new functionalities.}
        \item {Estimated work hours and tracked progress using Scrum methodology. (Scrum, Jira)}
        \item {Took over maintenance of the SaaS CRM (Customer Relationship Management) system they built and the full custom BPM (Business Process Manager) that was built to support it. (Salesforce, Apex, Marketing Cloud)}
        \item {Implemented new business features in coordination with other teams (backend, frontend and ERP).}
        \item {Designed and implemented features to make the GDPR compliant, in close collaboration with legal department.}
        \item {Updated programs as per user needs and developed codes that were in accordance to specifications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fullstack Developer} % Job title
    {Test, srl.} % Organization
    {Turin, Italy} % Location
    {Dec. 2015 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactored frontend and backend project code to improve platform performance and ease up the code handling and development. (PostgreSQL, PHP, Javascript)}
        \item {Implemented new business features based on the Google Maps APIs to plan trips.}
        \item {Optimized and expanded reporting system.}
        \item {Implemented a custom messaging system to deliver messages between users based on a custom built network infrastructure.}
        \item {Built the backend APIs system to integrate with the mobile application. (PHP, C)}
      \end{cvitems}
    }   

%---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {ST Microelectronics, inc.} % Organization
    {Turin, Italy} % Location
    {Jun. 2013 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Profiled a board equipped with MEMS sensors, focusing on build quality and sensor precision.}
        \item {Ran a technical assessment about the board compatibility with development of an inertial navigation system.}
        \item {Implemented a C\# application to read data coming from the board and plot the results in a GUI.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
