%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Engineering Manager} % Job title
{YoungCapital DASH, BV.} % Organization
{Hoofddorp, Netherlands} % Location
{Feb. 2022 - Current} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Manage 7 cross functional teams of different sizes with a grand total of 25 direct reports: Data Engineering, Business Intelligence, Cloud Platform and product development teams}
    \item {As part of the engineering leadership team, help set strategy and goals across multiple engineering teams through OKR and company wide initiatives}
    \item {Hire, inspire, manage, and grow cross-functional engineering teams, via career mentor \& development, 1-1s, feedback \& performance evaluation sessions}
    \item {Work closely with product counterparts, the CTO, staff engineers, and other stakeholders to execute initiatives that drive engineering excellence aligned with business objectives}
    \item {Drive continuous improvements in engineering standards, quality, and operational excellence while delivering business value through the adoption of SCRUM and other industry best practices}
    \item {Measure engineering efforts impact, track performance metrics, and identify areas for improvement while promoting a culture of innovation, accountability, collaboration, and continuous learning}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
  {Lead DevOps Engineer} % Job title
  {NEP The Netherlands, BV.} % Organization
  {Hilversum, Netherlands} % Location
  {Mar. 2021 - Jan. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Served as subject matter expert on Infrastructure as code for both clients and internal team members. (DevOps, Git, IaC)}
      \item {Drove infrastructure automation transition within the organization utilizing all solutions as code. (DevOps, Git, IaC)}
      \item {Used interpersonal and communication skills in interactions, enriching team collaboration, customer relationships on infrastructure as code projects. (Scrum, Jira, Ansible, Terraform)}
      \item {Developed and maintained distributed architecture solutions of production environment using cloud providers such as Google Cloud and AWS. (Kubernetes, Docker, Rancher, GCP)}
      \item {Worked with Infrastructure and SRE teams on adopting best practices, solutions and ways of utilising technologies effectively. (Ansible, Terraform)}
      \item {Created and maintained effective blueprints of the infrastructure and used automation and SaaS offerings, in order to modernise the way infrastructure and development teams use it. (CICD, Github Actions, Docker)}
    \end{cvitems}
  }

%---------------------------------------------------------    
  \cventry
  {Founder \& Engineering Manager} % Job title
  {Boxitonline B.V.} % Organization
  {Amsterdam, Netherlands} % Location
  {Nov. 2019 - Jan. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Lead cross-functional team from drafting the idea and prototype to market launch.}
      \item {Hands-on involved in leading the troubleshooting, architecting and implementing improved solutions that powers web environment in order to deal with growth requirements. (Nodejs, React, Serverless)}
      \item {Created organization's mission and vision statements for use by employees.}
      \item {Wrote financial forecasts and fund request applications to the European Community.}
      \item {Conducted target market research to scope out industry competition and identify advantageous trends. (Google Analytics)}
      \item {Created and monitored promotional approaches to increase sales and profit levels. (Google Analytics, HotJar)}
    \end{cvitems}  
  }  

%---------------------------------------------------------
  \cventry
    {DevOps Tech Lead} % Job title
    {Vandebron, BV.} % Organization
    {Amsterdam, Netherlands} % Location
    {Apr. 2018 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented solutions for platform resiliency and disaster recovery for business continuity, involving systems duplication, load balancing and multi-region provisioning. (Azure, AWS)}
        \item {Collaborated closely with product development teams and other stakeholders, using effective communication and active listening skills. (Slack, Jira, Scrum)}
        \item {Designed an overall service architecture and pipelines of the frontend with a micro-services architecture approach. (Nodejs, Scala, Docker)}
        \item {Migrated all the existing services from a VM based architecture onto docker containers running on a custom infrastructure. (D2iQ, Docker, Nodejs, Bash)}
        \item {Built fully automated CI/CD pipelines to build and deploy the frontend and backend applications. (Jenkins, GitHub Actions, Nodejs, Groovy)}
        \item {Integrated cloud environments into a centralized monitoring solution to improve awareness and control. (Elasticsearch, Logstash, Kibana)}
        \item {Maintained and expanded the infrastructure lifecycle in a IaC fashion, using Ansible and Terraform to deploy on AWS cloud. (Ansible, Terraform, EC2, S3)}
      \end{cvitems}
    }
      
%---------------------------------------------------------
  \cventry
    {Salesforce Tech Lead} % Job title
    {Vandebron, BV.} % Organization
    {Amsterdam, Netherlands} % Location
    {May. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided constant guidance, operational management and leadership to support the engineering team on a track of continuous improvement and growth.}
        \item {Recruitment, onboarding and staff management in collaboration with the CTO.}
        \item {Trained new team members, explaining the current system design and leading the team during development of new functionalities.}
        \item {Partner with PM, Sales, and Marketing to develop innovative features.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Salesforce Developer} % Job title
    {Vandebron, BV.} % Organization
    {Amsterdam, Netherlands} % Location
    {Jul. 2017 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Partner with PM, Sales, and Customers to develop innovative features.}
        \item {Estimated work hours and tracked progress using Scrum methodology. (Scrum, Jira)}
        \item {Implemented new business features in coordination with other teams (backend, frontend and ERP).}
        \item {Designed and implemented features to make the GDPR compliant, in close collaboration with legal department.}
        \item {Updated applications as per user needs and developed codes that were in accordance to specifications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fullstack Developer} % Job title
    {Test, srl.} % Organization
    {Turin, Italy} % Location
    {Dec. 2015 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented algorythms to handle high volumes of incoming data. (PostgreSQL, PHP, Javascript)}
        \item {Extracted metrics from collected data to empower customer's business overview. (PostgreSQL, PHP, Javascript)}
        \item {Improved system's quality adopting best practices of software development. (PostgreSQL, PHP, Javascript)}
        \item {Implemented new business features based on the Google Maps APIs.}
        \item {Designed and implemented the backend APIs system to integrate with the mobile application. (PHP, C)}
      \end{cvitems}
    }   

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {ST Microelectronics, inc.} % Organization
    {Turin, Italy} % Location
    {Jun. 2013 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Profiled a board equipped with MEMS sensors, focusing on build quality and sensor precision.}
        \item {Ran a technical assessment about the board compatibility with development of an inertial navigation system.}
        \item {Implemented a C\# application to read data coming from the board and plot the results in a GUI.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
